Predator summary

### 2023-02-09 reports/01_predators.qmd
Use Quarto project to fix output directory
Start on a basemap function

---
title: "Predator summary"
format:
  html:
    code-fold: true
editor: visual
---

@@

snpt_sf <- predators_agg %>% 
  filter(species == "SNPT",
         year == 2016) %>% 
  sf::st_as_sf(coords = c("lon_mean", "lat_mean"), 
               crs = sp::CRS("+proj=longlat +datum=WGS84"))

>>>>

---
title: "Predator summary"
format:
  html:
    code-fold: true
editor: visual
output-dir: "docs"
---

@@

snpt_sf <- predators_agg %>% 
  filter(species == "SNPT",
         year == 2016) %>% 
  latlon_to_sf(coords = c("lon_mean", "lat_mean"))
